---
output:
  md_document:
    variant: markdown_github
---
```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# foofactor
The goal of foofactor is to [practice in the development of an R package](http://stat545-ubc.github.io/packages00_index.html). Functions include:

- `fbind()`
- `freq_out()`
- `should_factor_be_factor()`

## Installation
You can try out the dev version from GitHub with:
```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("csiu/foofactor")
```

## Usage
We first load the package
```{r}
library(foofactor)
```
In the package, I have also provided example factors
```{r}
exampleFactor1
exampleFactor2
exampleFactor3
```

### `fbind` - Bind two factors together
```{r}
fbind(exampleFactor1, exampleFactor2, level.as.appears = TRUE)
```
Here we bind together two factors. When we specify `level.as.appears = FALSE`, the order of the levels will seemingly be random. 

### `freq_out` - Create a frequency table for a factor
```{r}
freq_out(exampleFactor3, n.sort = "descending")
```
`n.sort` can take the values of `ascending`, `descending`, or `NULL` (where `NULL` refers to the default behaviour without sorting on the frequency column).

### `should_factor_stay_factor` - Should factor stay as factor?
```{r}
should_factor_stay_factor(exampleFactor3)
```
Here we ask whether it makes sense for a factor to stay as a factor e.g. if the number of unique values of a factor is equal to the length, then maybe the factor would be better suited as a character vector.

## Vignettes
For more information, please check out the vignette at:
```{r eval=FALSE}
vignette("foofactor", package = "foofactor")
```

## Acknowledgements
- [Jenny Bryan](http://github.com/jennybc) and [STAT 545/547M](http://stat545-ubc.github.io/packages00_index.html) for teaching and providing resources to simplify writing an R package
- [parent `foofactors` repo](https://github.com/STAT545-UBC/foofactors)
