---
title: "foofactor"
author: "csiu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of foofactor -- based on [foofactors](https://github.com/STAT545-UBC/foofactors) -- is to practice in the development of an R package^[[Write your own R package](http://stat545-ubc.github.io/packages00_index.html)]. Functions include:

- `fbind()`
- `freq_out()`
- `should_factor_be_factor()`

## Installation

```{r eval=FALSE}
# install.packages("devtools")
devtools::install_github("csiu/foofactor")
```

```{r}
library(foofactor)
```

## Example data
Here the number of factors and number of factor levels are the same:
```{r}
exampleFactor1
exampleFactor2
```

Here factors are repeated:
```{r}
exampleFactor3
```

## `fbind` - Bind two factors together
Here we bind together two factors and by default the factor levels are combined as they appear e.g. `level.as.appears = TRUE`:
```{r}
fbind(exampleFactor1, exampleFactor2)
```

When we let `level.as.appears = FALSE`, the order of the levels will seemingly be random:
```{r}
fbind(exampleFactor1, exampleFactor2, level.as.appears = FALSE)
```

## `freq_out` - Create a frequency table for a factor
Here we create a frequency table for a factor:
```{r}
freq_out(exampleFactor3)
```

We can sort this table according to ascending frequencies:
```{r}
freq_out(exampleFactor3, n.sort = "ascending")
```

We can sort this table according to descending frequencies:
```{r}
freq_out(exampleFactor3, n.sort = "descending")
```

`n.sort` can therefore take the values of `ascending`, `descending`, or `NULL` (where `NULL` refers to the default behaviour without sorting on the frequency column).

## `should_factor_stay_factor` - Should factor stay as factor?
Here we ask whether it makes sense for a factor to stay as a factor e.g. if the number of unique values of a factor is equal to the length (such as in `exampleFactor1`), then maybe the factor would be better suited as a character vector so the factor should not stay as a factor.

```{r}
should_factor_stay_factor(exampleFactor1)
```

On the other hand, if the number of unique values of a factor does not equal the length (such as in `exampleFactor3`), then maybe the factor would be better suited to stay as a factor.

```{r}
should_factor_stay_factor(exampleFactor3)
```
